---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

[![Travis-CI Build Status](https://travis-ci.org/CannaData/CannaBarcode.svg?branch=master)](https://travis-ci.org/CannaData/CannaBarcode)

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

```{R, echo = FALSE, results = 'asis'}
cat(as.character(CannaBarcode::includeJsBarcode()))
```

# CannaBarcode

The goal of CannaBarcode is to wrap the [JsBarcode](https://github.com/lindell/JsBarcode) library, written by Johan Lindell, for R. This enables rendering of barcodes in R Markdown and Shiny. This enables generating receipts in markdown, which can compiled to HTML with `rmarkdown`, and then printed using Google Cloud Print using [`googlePrintr`](https://github.com/CannaData/googlePrintr).

## Installation

You can install CannaBarcode from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("CannaData/CannaBarcode")
```

## Example

### R Markdown

This is an example of how to render in R Markdown:

```{R, echo = FALSE, results = 'asis'}
cat(as.character(CannaBarcode::barcodeOutput("barcode")))
```

```{R, echo = FALSE, results = 'asis'}
cat(as.character(shiny::tags$script(CannaBarcode::barcode("barcode", 8675309))))
```

Look at the [raw README.rmd](https://raw.githubusercontent.com/CannaData/CannaBarcode/master/README.rmd) to see the code.

### Shiny

```{R, eval = FALSE}
library(shiny)
library(CannaBarcode)

ui <- fluidPage(
  # must include javascript dependencies
  CannaBarcode::includeJsBarcode(cdn = TRUE),
  numericInput("value", "Input a positive integer", 8675309, 0, 1000000),
  CannaBarcode::barcodeOutput("barcode")
)

server <- function(input, output, session) {
  output$barcode <- CannaBarcode::renderBarcode(
    input$value
  )
}

shinyApp(ui = ui, server = server)
```